---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# markovtext

<!-- badges: start -->
<!-- badges: end -->

A deeply unserious package for generating random text that mimics a given input text using Markov chains.

## Installation

You can install the development version of markovtext from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("chris31415926535/markovtext")
```

## Overview

The package has two main functions: `markovtext::get_word_freqs()` generates a word-frequency table, and `markovtext::generate_text()` uses that table to generate random text. It also includes a few sample word-frequency tables to get you started.   

## Example: Generating text based on built-in datasets

This package truly has something for everyone.

### For the Doug Ford superfans

Perhaps you are a [Doug Ford](https://en.wikipedia.org/wiki/Doug_Ford) superfan, and your only wish in life is for a never-ending source of wisdom from Ontario's 26th Premier. Today is your lucky day, for nirvana is only one function call away:

```{r}
dougford_text <- markovtext::generate_text(markovtext::wordfreqs_dougford_3grams, word_length = 100)
```

```{r eval=FALSE}
dougford_text
```

```{r echo = FALSE}
knitr::kable(dougford_text, col.names = "")
```

### For three-year-olds who just won't go to sleep

Or perhaps you're a beleaguered parent facing a three-year-old with an insatiable demand for Dr. Seuss bedtime stories. Again, I've got you covered:

```{r}
seuss_text <- markovtext::generate_text(markovtext::wordfreqs_catinthehat_3grams, word_length = 100)
```

```{r eval=FALSE}
seuss_text
```

```{r echo = FALSE}
knitr::kable(seuss_text, col.names = "")
```


## Example: Generating text based on your own inputs

### Creating a word-frequency table

To create a word-frequency table, you can supply a character vector or a data.frame with a column named "text."

Here we'll build our table based on this famous aphorism from the philosopher [James Robert Brown](https://en.wikipedia.org/wiki/James_Robert_Brown):

```{r example}
library(markovtext)

text <- "I can do wheelin', I can do dealin',
         But I don't do no damn squealin'.
         I can dig rappin', I'm ready! I can dig scrappin'.
         But I can't dig that backstabbin'."

wordfreqs <- markovtext::get_word_freqs(text, n_grams = 3)
```

### Generating text

Generating text is a simple call to `generate_text()`.

```{r}
new_text <- markovtext::generate_text(wordfreqs, word_length = 50)
```

```{r eval=FALSE}
new_text
```


```{r, echo = FALSE}
knitr::kable(new_text, col.names = "")
```

Note that leading and trailing punctuation is trimmed.
